MSDS 6306: Doing Data Science - Case Study 01 - Beers/Breweries Dataset

### 2020-10-11 MSDS6306_DDS_CaseStudy01-Beersdataset.Rmd
Rmd file

#Added Alaska to states as the states data does not include Alaska (Hawaii not in data so did not include in below data)
Alaska <- read.csv(choose.files(),header = T,sep = ",",na.strings = "NA",
                          fill = TRUE);
states <- rbind(states,Alaska)

@@

#state center longitude and latitude (read data from csv file)
st_center <- read.csv(choose.files(),header = T,sep = ",",na.strings = "NA",
                          fill = TRUE);
# state names changed to lower case
st_center$region <- tolower(st_center$region)

#map.df1 merges state center with Breweris count data
map.df1 <- merge(st_center,Brewcount2, by="region", all.x=T)

# Adding state names and Breweries count data by state 
Nplot <- plot + geom_point(data=map.df1, aes(x=long, y=lat, 
                                             size = Breweries_Count, group = region),
                           show.legend = FALSE) + 
  geom_text(aes(x=long, y=lat,label=abb,group = region), data = map.df1,vjust=-1.2) +
  geom_text(aes(x=long, y=lat,label=Breweries_Count,group = region), 
            data = map.df1,vjust=1.6)

>>>>

#Added Alaska to states as the states data does not include Alaska (Hawaii not in data so did not include in below data)
Alaska <- read.csv("https://raw.githubusercontent.com/VenkataVanga/MSDS-6306/main/Alaska.csv",header = T,sep = ",",na.strings = "NA",
                          fill = TRUE);
states <- rbind(states,Alaska)

@@

#state center longitude and latitude (read data from csv file)
st_center <- read.csv("https://raw.githubusercontent.com/VenkataVanga/MSDS-6306/main/long_lat_statecenter.csv",header = T,sep = ",",na.strings = "NA",
                          fill = TRUE);
# state names changed to lower case
st_center$region <- tolower(st_center$region)

#map.df1 merges state center with Breweries count data
map.df1 <- merge(st_center,Brewcount2, by="region", all.x = T)

# Adding state names and Breweries count data by state 
Nplot <- plot + geom_point(data=map.df1, aes(x=long, y=lat, 
                                             size = Breweries_Count, group = region),
                           show.legend = FALSE) + 
  geom_text(aes( x= long, y = lat,label = abb.x, group = region), 
            data = map.df1, vjust=-1.2) +
  geom_text(aes(x = long, y = lat, label = Breweries_Count, group = region), 
            data = map.df1,vjust=1.8)
